InteroceptionStudy_GPValidation

### 2021-09-14 IAPS_PREPROCESSING_2021_1_56_357_611_616.Rmd
idk

@@

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 30
  for (f in 1:length(hdfFilesList)) {

@@

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")

@@

@@

range(tmp.df, na.rm = TRUE)
tmp.df2$y_outside<-NULL

@@

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

@@

@@

# plot diagnosis
ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)

ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
    geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response =   max(gsr_basCor))

# gsr response for every bit
unique(tmp.df3$screencontent)

@@

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial = tmp.df3$trialUnq

@@

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

@@

@@

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3<- tmp.df3%>%
  # arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo,screencontent)%>%
  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

colnames(tmp.df4)
write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')

@@

unique(tmp.df4$trigger2)
unique(tmp.df4$trigger)
unique(tmp.df4$tNo)

@@

write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')

write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
# 
# head(tmp.df4_sum)
# unique(tmp.df4_sum$tNo)

@@

@@

@@

  colnames(for_gazepath)

@@

  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")

@@

right eye x coord: right_gaze__cor_pix
right eye y coord: right_gaze_x_cor_pix
didtance: distance (mm)

@@

read parsed data
```{r}
read_parsed <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

@@

db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
unique(db_parsed$screencontent_no)
db_parsed$ssid<- substr(db_parsed$Participant, 4,6)

@@

# this might be needed for tempoal analisys
write_csv(db_parsed, 'db_parsed.csv')
write_csv(db_parsed, 'db_parsed_346_355.csv')

@@

View(db_parsed)

@@

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')

@@

@@

@@

@@

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
# now read them
db_beh <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_plus_beh(.))

# problem file
# db328$condition<-db328$ï..condition

@@

db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

# 
# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
#                 use.names = TRUE, idcol = "filename")
# 
# 
# 
# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

@@

# problem
db328$filename<- as.character(db328$filename)
db328$ssid<- as.character(db328$ssid)

@@

db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
db_beh2$tNo<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$trialsPract.thisTrialN, db_beh2$trialIAPS.thisTrialN)
unique(db_beh2$tNo)
db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)

@@

colnames(db_beh3_301_309)

db_beh3$trigger<-NULL
db_beh3_301_309$triggeracq<- NULL

db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"

@@

# db_beh3$triggeracq<- NULL

library(readr)
db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
View(tmp_df4300_sum_full)

db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
colnames(db_beh300)

@@

db_beh3$ssid <- as.numeric(db_beh3$ssid)
# rm(tmp.df4_sum_full_t)

@@

@@

@@

STAI:: 5nzr
AQ:7uqw
STAIS: 8rfo
Demog: 8zto
BVAQ: 83b1
BPQ: bbc4
DASS: chif
IQ: esh8
IAS: jvi8
TAS:pdlt
demog_meantal health: v2gn

@@

db_selfrep <- read_csv("intero_selrep.csv")
library(readxl)
db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
# View(db_self_rep_345_356_final)

db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)

@@

View(tmp.df4_sum_full)
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)

colnames(tmp.df4_sum_full)
```

@@

@@

@@

# now read them
db_leda <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda(.))

@@

db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))

colnames(tmp.df4_sum)
colnames(db_leda)

@@

@@

@@

tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))

# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)

@@

trigger<- db_leda2 %>%
  subset(ssid == 348)%>%
  select(order, Event.NID, trigger,Event.Nr)
```

@@

# check stiom screen
tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')

@@

# is objective arousal and self report arousal correated
tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/345_456/CDA")

@@

# now read them
db_leda_bio <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda_bio(.))

write_csv(db_leda_bio, 'db_leda_bio.csv')
write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')

@@

@@

@@

@@

db_leda_bio$BIO_Event.NID<- NULL
db_leda_bio$BIO_filename<- NULL

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
library(readxl)
library(dplyr)
# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

@@

unique(db_HR_bio1no328$tNo)
```

>>>>

hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/346_357_611_616"

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/346_357_611_616")

@@

    return(message('No HDF5 files found in the directory provided.'))
  }
   # f = 30
  for (f in 1:length(hdfFilesList)) {

@@

# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/356_357_611_616")

@@

tmp.df2$ssid[tmp.df2$ssid == 311] <- 611
tmp.df2$ssid[tmp.df2$ssid == 312] <- 357
unique(tmp.df2$ssid)

@@

# range(tmp.df, na.rm = TRUE)
tmp.df2$y_outside<-NULL

@@

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
# natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

@@

# rest
ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3$gsr_ms[tmp.df3$gsr_ms == "Inf"]<-NA

# gsr for leda
colnames(tmp.df3)
db_GSR_backup<- db_GSR
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51,52 ))
db_GSR$tNo<- NULL
colnames(db_GSR_backup)
# unique(db_GSR_backup$trigger)
colnames(db_GSR)

@@

# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/356_357_611_616")

@@

# plot diagnosis
# takes a bit - 
ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

# plotting rest
 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)

 # just stim
ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
    geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

range(tmp.df3$gsr_basCor)
tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response = max(gsr_basCor, na.rm = TRUE))

range(tmp.df3$gsr_response, na.rm = TRUE)
unique(tmp.df3$gsr_response, na.rm = TRUE)

tmp.df3$gsr_response[tmp.df3$gsr_response == "-Inf"]<- NA
# gsr response for every bit
unique(tmp.df3$screencontent)

@@

# note that smothing and interpolating is order dependent so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial <- tmp.df3$trialUnq

@@

subset(tmp.df3, tNo == 20 & ssid == 357)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 357)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

@@

range(max_pup$MAD)
range(max_pup$speed)
table(is.infinite(max_pup$MAD))
tmp.df3_backup<- tmp.df3

@@

  subset(tmp.df3,  tNo == 10 & ssid == 357)%>%
ggplot(aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_line(aes(y =pup_interp_mad), color = "red")+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo,screencontent)%>%
  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 611) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 615) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 356) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

colnames(tmp.df4)
# write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')

write_csv(tmp.df4, 'interodata_clean_gp_356_357_611_616.csv')

@@

unique(tmp.df4$trigger2)
unique(tmp.df4$trigger)
unique(tmp.df4$tNo)
unique(tmp.df4$ssid)

@@

# write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')

# write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
write_csv(tmp.df4_sum, 'interodata_clean_gp_356_357_611_616.csv')

# interodata_clean_gp_356_357_611_616.csv
# 
# head(tmp.df4_sum)
# unique(tmp.df4_sum$tNo)

@@

# 616 seesm to have vey poor data fr eyetracking - exclude

@@

  for_gazepath<- subset(for_gazepath, ssid!= 616)

@@

  colnames(for_gazepath)
  unique(for_gazepath$ssid)

@@

  # setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")

  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")

@@

right eye x coord: right_gaze_x_cor_pix
right eye y coord: right_gaze_y_cor_pix
didtance: distance (mm)

@@

read parsed data
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")

read_parsed <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_parsed_backup<- db_parsed

@@

db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
unique(db_parsed$screencontent_no)
db_parsed$ssid<- substr(db_parsed$Participant, 4,6)
unique(db_parsed$ssid)

@@

# this might be needed for tempoal analisys
# write_csv(db_parsed, 'db_parsed.csv')
# write_csv(db_parsed, 'db_parsed_346_355.csv')
write_csv(db_parsed, 'db_parsed_356_357_611_615.csv')

@@

# View(db_parsed)

@@

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
# write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
# write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')
write_csv(db_parsed_summarised2, 'db_parsed_summarised_356_357_611_615.csv')

@@

unique(tmp.df4_sum$ssid)
tmp.df4_sum_full_backup<- tmp.df4_sum_full

@@

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo, screencontent_no)
tmp.df4_sum_full
```

@@

# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/356_357_611_616")

@@

# now read them
db_beh_backup<- db_beh

db_beh <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_plus_beh(.))

unique(db_beh$filename)

# problem file

# db328$condition<-db328$ï..condition

@@

# db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
#                 use.names = TRUE, idcol = "filename")
# 
# 
# 
# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

@@

# problem file
db328$filename<- as.character(db328$filename)
db328$ssid<- as.character(db328$ssid)

@@

db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
db_beh2$tNo<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$trialsPract.thisTrialN, db_beh2$trialIAPS.thisTrialN)
unique(db_beh2$tNo)

db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)

@@

# colnames(db_beh3_301_309)

db_beh3$trigger<-NULL
# db_beh3_301_309$triggeracq<- NULL

# db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"

@@

```
Probem file
# db_beh3$triggeracq<- NULL

library(readr)

# db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
# View(tmp_df4300_sum_full)

# db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
# colnames(db_beh300)

@@

# rm(tmp.df4_sum_full_t)

@@

```{r}
db_beh3$ssid <- as.numeric(db_beh3$ssid)

tmp.df4_sum_full_backup_before_beh<- tmp.df4_sum_full

@@

unique(tmp.df4_sum_full$ssid)

@@

STAI:: 5nzr
AQ:
STAIS: 8rfo
Demog: 8zto
BVAQ: 83b1
BPQ: bbc4
DASS: chif
IQ: esh8
IAS: jvi8
TAS:pdlt
demog_meantal health: v2gn

@@

db_selfrep <- read_csv("intero_selrep.csv")
library(readxl)
db_selfrep_backup<- db_selfrep
db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")

library(readr)

db_selfrep <- read_csv("db_self_rep_356_357_611_616_final.csv")
View(db_selfrep)
# View(db_self_rep_345_356_final)
colnames(db_selfrep)

tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)

unique(db_selfrep$ssid )

tmp.df4_sum_full_backup_before_selfrep<- tmp.df4_sum_full
db_selfrep$`Participant Private ID.x.x`<- NULL

@@

View(tmp.df4_sum_full)
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_356_357_611_616.csv')
# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)
unique(tmp.df4_sum_full$ssid)
colnames(tmp.df4_sum_full)

db_selfrep
```

@@

>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/3052_356/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])

>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/356_457_611_616/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])

>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/ledalab-349/', 'open','biopac','downsample', 200, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2]

@@

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/356_457_611_616/Processed")

@@

# now read them

db_leda_backup<- db_leda

db_leda <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda(.))

@@

db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
unique(db_leda$ssid)
colnames(tmp.df4_sum)
colnames(db_leda)

@@

tmp.df4_sum2_backup<- tmp.df4_sum2

@@

db_leda2_backup<- db_leda2

@@

nrow(tmp.df4_sum2)
tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
nrow(tmp.df4_sum_full)
# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
unique(tmp.df4_sum_full$ssid)

@@

# trigger<- db_leda2 %>%
#   subset(ssid == 348)%>%
#   select(order, Event.NID, trigger,Event.Nr)
```

@@

# check stiom screen
tmp.df4_sum_full_stim_baclup<- tmp.df4_sum_full_stim

tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')

@@

# is objective arousal and self report arousal correated
tmp.df4_sum_full_stim
tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')

@@

>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/ledalab-349/', 'open','biopac','downsample', 200, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2]

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/356_357_611_616/CDABIO")

@@

# now read them

db_leda_bio <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda_bio(.))

view(db_leda_bio)

write_csv(db_leda_bio, 'db_leda_bio.csv')
write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')
write_csv(db_leda_bio, 'db_leda_bio_356_357_611_616 CDA.csv')

@@

View(trigger)

@@

  nrow(db_leda_bio)

  db_leda_bio_beforetrig<- db_leda_bio

@@

db_leda_bio_backup_beforename<- db_leda_bio

@@

db_leda_bio$BIO_Event.NID <- NULL
db_leda_bio$BIO_filename <- NULL

nrow(tmp.df4_sum_full)
nrow(db_leda_bio)

tmp.df4_sum_full_bio_backup<- tmp.df4_sum_full_bio
tmp.df4_sum_full$ssid<- as.character(tmp.df4_sum_full$ssid)

@@

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")

setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/356_357_611_616")
library(readxl)
library(dplyr)
# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")

@@

# unique(db_HR_bio2$tNo)
